```{r libs  }
require(tidyverse)
require(tidyquant)

```

here I will import some long term data from BB data

first let me try the international commodity price

```{r icim  }
library(readxl)
path <- "./RAWDATA/statisticaltable_dec2016.xls"
int.price.raw <- read_excel(path, sheet="Table XXII",range=cell_rows(28:57), col_names=FALSE)
```

Now time to name the variables

```{r nv  }
var.labs <- c(month="Calendar months",
	      gold="Gold price, US$/Troy Ounce, UK(London)",
	      coal="Coal price, US$/MT,Australia", 
	      iron_ore="Iron Ore, US$/MT, China(CFR Tianjin Port",
	      petroleum1="Petroleum, US$/Barrel, Dubai Fateh",
	      petroleum2="Petroleum, US$/Barrel, UK Brent",
	      cotton="Cotton, US cents/pound, Liverpool index",
	      super_pphate="Super phosphate, US$/MT, USA, gulf ports",
	      urea="Urea, US$/MT, Ukraine",
	      rice1="Rice, US$/MT, Thailand(Bangkok)",
	      rice2="Rice, US$/MT, Thailand",
	      wheat1="Wheat, US$/MT, Australia",
	      wheat2="Wheat, US$/MT, United States",
	      wheat3="Wheat, US$/MT, Argentina",
	      palm_oil1="Palm Oil, US$/MT, Malaysia, NW Europe",
	      palm_oil2="Palm Oil, US$/MT, Malaysia",
	      soya_bean1="Soya Bean, US$/MT, USA(Rotterdam)",
	      soya_bean2="Soya Bean Oil, US$/MT, All origins (Dutch ports)",
	      sugar1="Sugar, US cents/pound, EU Import Price",
	      sugar2="Sugar, US cents/pound, Free Market",
	      sugar3="Sugar, US cents/pound, US Import price")

names(int.price.raw) <- names(var.labs)
int.price <- int.price.raw %>% 
		filter(!month %in% c(2015,2016))
int.price.14.16  <- int.price %>% 
		mutate(year=c(rep(2014,12),rep(2015,12),rep(2016,4)))
save(int.price.14.16, file="./RDATA/int_price_14_16.RData")
```

Now let's bring in  another data set

```{r im12  }
path <- "./RAWDATA/statisticaltable_2014.xls"
int.price.raw.13 <- read_excel(path, sheet="Table XXIV",range=cell_rows(27:38), col_names=FALSE)
names(int.price.raw.13) <- names(var.labs)
int.price.13 <- int.price.raw.13 %>% 
		    mutate(year=rep(2013,12))
save(int.price.13, file="./RDATA/int_price_13.RData")
```

Now time to combine those prices

```{r com  }
int.price.13.16 <- rbind(int.price.13, int.price.14.16)
save(int.price.13.16, file="./RDATA/int_price_13_16.RData")
```
September 19, 2017  10:14 

now let's check what's in the above int.price.12.16 

10:34 there was definitely some problem which has been fixed and has been changed to int.price.13.16

```{r chi  }
load("./RDATA/int_price_12_16.RData")
load("./RDATA/int_price_12.RData")
load("./RDATA/int_price_14_16.RData")
```


now adding up rest of the datasets

next target is statisticaltable_june13.xls

```{r stab  }
path <- "./RAWDATA/statisticaltable_june13.xls"
int.price.11.12.raw <- read_excel(path, sheet="Table XXIV", range=cell_rows(25:49), col_names=FALSE)
names(int.price.11.12.raw) <- names(var.labs)
int.price.11.12  <- int.price.11.12.raw %>% 
			filter(!month %in% 2012) %>% 
			mutate(year=c(rep(2011,12),rep(2012,12)))

save(int.price.11.12, file="./RDATA/int_price_11_12.RData")
```

now time to combine this with previous data

```{r c12  }
int.price.11.16 <- rbind(int.price.11.12, int.price.13.16) %>% 
                         slice(1:60)  # to start 2016 afresh from begining
save(int.price.11.16, file="./RDATA/int_price_11_16.RData")
load("./RDATA/int_price_11_16.RData")
```

```{r stab1  }
path <- "./RAWDATA/statisticaltable_sep2017.xlsx"
int.price.16.17.raw <- read_excel(path, sheet="Table XXII", range=cell_rows(33:50), col_names=FALSE)
names(int.price.16.17.raw) <- names(var.labs)
int.price.16.17  <- int.price.16.17.raw %>% 
			filter(!month %in% 2017) %>% 
			mutate(year=c(rep(2016,12),rep(2017,5)))

save(int.price.16.17, file="./RDATA/int_price_16_17.RData")
```

now combine with again of rest of the data


```{r stab3  }
int.price.11.17 <- rbind(int.price.11.16, int.price.16.17)
int.price.11.17  <- int.price.11.17 %>% 
		    mutate(yrmon=paste(year,month,sep="-"),
			   yrmon=as.yearmon(yrmon,format="%Y-%B")
			   ) %>% 
		    mutate_at(vars(gold:sugar3),as.numeric)

save(int.price.11.17, file="./RDATA/int_price_11_17.RData")
```

Now time to draw some charts of international rice price

```{r intchart  }
load("./RDATA/int_price_11_17.RData")
#Sep 26 10:39, upon loading just noticed that still year is there, let's get rid of that
int.price.11.17 <- int.price.11.17 %>% 
			select(-year, -month)
int.price.11.17 %>% 
    ggplot(aes(x=yrmon,y=rice2))+
	    geom_line()
```

lets zoom into the last two years

```{r ch2  }
int.price.11.17 %>% 
    filter(year(yrmon) > 2014) %>% 
    ggplot(aes(x=yrmon,y=rice2))+
	    geom_line()

```


It seems that international price is falling rapidly. so its great. then why the crisis? 
Just because of domestic failings? 

let's compare the above internation price with price we get from FPMU database


```{r fpi  }
url <- read_html("http://fpmu.gov.bd/fpmu-database/0204.htm")
int.price.fpmu.raw <- url  %>% 
			html_node("table") %>% 
			html_table(fill=TRUE) %>% 
			slice(8:112)
var.names.int.fmpu <- c("time","us.rice1","us.rice2","us.rice3","thai.rice1", "thai.rice2","thai.rice3","thai.rice4","vietnam.rice","us.wheat1","us.wheat2","argentina.wheat")

names(int.price.fpmu.raw)  <-   var.names.int.fmpu
save(int.price.fpmu.raw, file="./RDATA/int_price_fpmu_raw.RData")

```

Now let's separate the yearly and monthly data

```{r sep  }
int.price.fpmu.yr  <- int.price.fpmu.raw %>% 
			slice(1:14)
save(int.price.fpmu.yr, file="./RDATA/int_price_fpmu_yr.RData")

int.price.fpmu.mo  <- int.price.fpmu.raw %>% 
			slice(15:102)
int.price.fpmu.mo2  <- int.price.fpmu.mo %>% 
                      filter(!grepl("FY",time)) %>% 
			mutate(time=sub("(.{3})(.*)\\s(\\d+)","\\1-\\3",time),
			       time=sub("\\.","-",time),
			       time=sub("\\s","-",time),
			       time=sub("([a-zA-Z]{3})([a-zA-Z]*)(\\d+)","\\1-\\3",time),
			       time=as.yearmon(time,"%b-%Y")
			       ) 
int.price.fpmu.mo2  <- int.price.fpmu.mo2 %>% 
			   mutate_at(vars(-time),as.numeric) 
save(int.price.fpmu.mo2, file="./RDATA/int_price_fpmu_mo2.RData")



```


Now time to plot all the prices


```{r inpfp  }
load("./RDATA/int_price_fpmu_mo2.RData")
int.price.fpmu.mo2 %>% 
      gather(series,price,-time) %>% 
      ggplot(aes(x=time,y=price)) +
      geom_line() +
      facet_wrap(~series)
```


In the above, we find that almost all the prices are falling

now to have more confirmation let's zoom in last few years

```{r inpfpl  }
int.price.fpmu.mo2 %>% 
      filter(year(time) > 2013) %>% 
      select(time, thai.rice1,us.rice1,vietnam.rice) %>% 
      gather(series,price,-time) %>% 
      ggplot(aes(x=time,y=price)) +
      geom_line() +
      facet_wrap(~series, ncol=1)

```

now let's pick a single series and see what happens



earlier data are in pdf format, so we will have to use the tabulizer package

```{r tabu  }
library(tabulizer)
 locate  <-  "./RAWDATA/june11/econtrdsxxiv.pdf"
out  <- extract_tables(locate,page=1)
```

it seems that it did not work at all

July 19, 2017  20:26:

at this point i will take a little digression since I got wealth of information in FPPU data base in the 
following:

# Average wholesale price of coarse rice

```{r scr  }
library(rvest)
rice.price <- read_html("http://fpmu.gov.bd/fpmu-database/0201.htm")
rice.price.df  <- rice.price %>% 
			html_node("table") %>%
			html_table(fill=true) %>% 
			slice(5:18)
names(rice.price.df) <- slice(rice.price.df,1)
rice.price.df <- slice(rice.price.df,-1) # converted to variable name
rice.price.df <- slice(rice.price.df,-13) # 

save(rice.price.df, file="./RDATA/rice_price_df.RData")   

```

## Sep 20, 2017 

### 08:19 

The above data set is quite ready for further manipulation. Let's have a look at the current situation

```{r cs  }
load("./RDATA/rice_price_df.RData")
head(rice.price.df)
```

now i am planning to use the tidyr package to gather the data

```{r tdp  }
library(tidyr)
rice.td <- rice.price.df %>% 
	    gather(FY,amount,-Month)

rice.td2  <- rice.td %>% 
		mutate(year=ifelse(Month %in% c("July","August","September","October","November","December"),sub("(.+)\\/(.+)","\\1",FY),sub("(.{2})(.+)\\/(.+)","\\1\\3",FY))) %>% 
		select(-FY)
save(rice.td2, file="./RDATA/rice_td2.RData")

```

### 09:28

now so far so good, i managed to come up with a workable solution, now its time to convert the year and month into an yearmon object

```{r ym2  }
rice.td3  <- rice.td2 %>% 
		mutate(year=replace(year,year=="1900","2000"),
		       yrmon=paste(year,Month,sep="-"),
		       yrmon=as.yearmon(yrmon,"%Y-%B"),
		       amount=as.numeric(amount)
		       ) %>% 
		select(-Month,-year) %>% 
		select(yrmon,amount) # rearranging
save(rice.td3, file="./RDATA/rice_td3.RData")
```


Now let's make an attempt to draw a chart

### 10:00

```{r ch  }
load("./RDATA/rice_td3.RData")
rice.td3 %>% 
     ggplot( aes(x=yrmon,y=amount)) +
		geom_line()	
```

I tried different way but don't know what the hell the problem is but it seems that there is always it starts from 1900 and it messes up everything. so i had to filter in above. in the following i am going to filter it so that i can save it in a data.frame. (Update: this comment is no longer relevant, it has been fixed)

```{r fixdf  }
#rice.td4  <- rice.td3 %>% 
	#	filter(year(yrmon)>1994) 
```

### 12:46

Breaking news , i discovered the problme, stemmed from 1900/00 dates converted to 1900. all I have to is filter those to 2000 in rice.td2.  so the above rice.td4 is no longer required

okay great, now we are on our way. 


Now let's check the data on last five years
```{r dt5  }
rice.td3 %>% 
    filter(year(yrmon) > 2012) %>% 
     ggplot( aes(x=yrmon,y=amount)) +
		geom_line()	

```

now  let's first check monthly variation in prices

even before that, let's convert those to yearly prices





```{r yr  }
rice.yr <- rice.td3 %>% 
	    tq_transmute(select=amount,
			 mutate_fun=apply.yearly,
			 FUN=median
			) 

```

Now time to plot the data

```{r yrp}
rice.yr %>% 
    ggplot(aes(x=yrmon,y=amount))+ 
    geom_line()
```

Seems like high frequency changes but I would like to find yearly changes

now very simply we could just do this

```{r delt  }
Delt(rice.yr$amount)
```

But if we want to have it in tidy format

```{r deltTD  }
rice.yr.d <- rice.yr %>% 
    tq_transmute(select=amount,
		 mutate_fun=Delt,
		 col_rename="amount") %>% 
                 filter(!is.na(amount))
```

Now let's plot these changes

```{r deltplot  }
rice.yr.d %>% 
	ggplot(aes(x=yrmon, y=amount,fill=amount)) +
	    geom_bar(stat="identity")
```

doesn't seem to have much insight, aman price, for the last few years have been , falling, let's zoom in last couple of years. Update: its not aman price, its the course rice

```{r lstc  }
rice.td3 %>% 
    filter(year(yrmon) > 2011) %>%
    ggplot(aes(x=month(yrmon), y=amount,color=as.factor(year(yrmon))))+
	   geom_line() +
	   facet_wrap(~as.factor(year(yrmon))) +
	   theme_tq()

```

It seems that from May, 2016 price has been steadily rising. 

### 19:43 

Now let's check whether there is any other data source on other rice category

I don't seem to find any other rice information in FPMU but for let's check on the production side

and import data from http://fpmu.gov.bd/fpmu-database/0101.htm

# Food grain availability in Bangladesh

```{r improd  }
web <- "http://fpmu.gov.bd/fpmu-database/0101.htm"

foodgrain.bd.raw <- read_html(web) %>%
		    html_node("table") %>% 
		    html_table(fill=TRUE) %>%
		    slice(10:29) 

```

So got the basic data up and running and now time to name the variables

```{r nv  }
var.names <- c("FY","rice.gross.prod","wheat.gross.prod","rice.net.prod","wheat.net.prod",
	       "population","rice.pri.imp","wheat.pri.imp","rice.pub.dist","wheat.pub.dist",
	       "rice.procure","wheat.procure", "rice.net.dom.avail", "wheat.net.dom.avail")

foodgrain.bd.raw2  <- foodgrain.bd.raw %>% 
			select(1,2,3,5,6,8,10,11,13,14,16,17,19,20)
names(foodgrain.bd.raw2)  <- var.names
foodgrain.bd  <- foodgrain.bd.raw2 %>% 
		    mutate_at(var.names[-1],as.numeric) %>% 
		    mutate(FY=sub("(.+)/(.+)","FY\\2",FY),
			   FY=factor(FY,levels=FY) # this is important to keep the years in right sort order
			   )
save(foodgrain.bd, file="./RDATA/foodgrain_bd.RData")
```

so here are the variable names


```{r vn  }
names(foodgrain.bd)
```
Let's have a quick graph of all the variables

```{r allvars  }
load("./RDATA/foodgrain_bd.RData")
foodgrain.bd %>% 
    gather(vars,value, -FY) %>% 
    ggplot(aes(x=FY,y=value)) +
	   geom_line(group="") +
	   facet_wrap(~vars, ncol=3,scale="free_y")
```

## Rice production

let's have an overall look at gross production

```{r rprod  }
foodgrain.bd %>% 
    ggplot(aes(x=FY,y=rice.gross.prod)) +
	geom_line(group="")
```
let's have a look at the last five year's situation


```{r lf  }
foodgrain.bd %>% 
    slice(16:20) %>% 
    ggplot(aes(x=FY,y=rice.gross.prod)) +
	geom_line(group="")

```

How about private import?

```{r pi  }
foodgrain.bd %>% 
    slice(16:20) %>% 
    ggplot(aes(x=FY,y=rice.pri.imp)) +
	geom_line(group="")

```

There is sharp decline in private import between FY15 and FY16


Let's also have a look at procurement data


```{r pd  }
foodgrain.bd %>% 
    slice(16:20) %>% 
    ggplot(aes(x=FY,y=rice.procure)) +
	geom_line(group="")


```

this also experienced sharp fall

now i want to calculate net availability of rice

```{r netav  }
#foodgrain.bd2  <- foodgrain.bd %>% 
#	    mutate(rice.net.avail=rice.net.prod+rice.pri.imp-rice.pub.dist+rice.procure)
```

The above calculation did not match, sw we gave up the effort and included all the net availability of the information. now let's check what's happening

```{r neta  }
foodgrain.bd %>% 
    slice(16:20) %>% 
    ggplot(aes(x=FY,y=rice.net.dom.avail)) + 
               geom_line(group="")
```

in the above we see that net rice availability is going down


Let's have a look at monthly data of public closing stock of rice

```{r pubRice  }
url  <- read_html("http://fpmu.gov.bd/fpmu-database/0601.htm")
rice.pub.cl.mo.raw <- url %>% 
		  html_node("table") %>% 
		  html_table() %>% 
		  slice(4:16)
names(rice.pub.cl.mo.raw)  <- rice.pub.cl.mo.raw %>% 
				    slice(1)
rice.pub.cl.mo.raw2  <- rice.pub.cl.mo.raw %>% 
			slice(-1)
rice.pub.cl.mo  <- rice.pub.cl.mo.raw2 %>% 
		     gather(FY,amount,-Month) %>% 
		mutate(year=ifelse(Month %in% c("July","August","September","October","November","December"),sub("(.+)\\/(.+)","\\1",FY),sub("(.{2})(.+)\\/(.+)","\\1\\3",FY))) %>% 
		  select(-FY) %>% 
		  mutate(year=replace(year, year=="1900", "2000"),
                         yrmon=paste(Month,year,sep="-"),
			 yrmon=as.yearmon(yrmon,"%B-%Y"),
			 amount=as.numeric(amount)
			 ) %>% 
		  select(yrmon,amount) 

rice.pub.cl.mo  <- rice.pub.cl.mo %>% 
                      filter(!is.na(amount))
		    

save(rice.pub.cl.mo, file ="./RDATA/rice_pub_cl_mo.RData")
load("./RDATA/rice_pub_cl_mo.RData")
```

Now let's view the chart


```{r pubstock  }
rice.pub.cl.mo %>% 
    filter(year(yrmon) > 2011) %>% 
    ggplot(aes(x=yrmon,y=amount)) +
	    geom_line()
```

Let's have a look at the yearly pattern


```{r pubstock4  }
rice.pub.cl.mo %>% 
    mutate(mo=month(yrmon),
	   yr=year(yrmon)) %>% 
    filter(yr  > 2011) %>% 
    ggplot(aes(x=mo,y=amount)) +
	    geom_line() +
	    facet_wrap(~yr)
```




the above is quite zigzag, kind of random pattern, so let's smoothen it by converting to yearly

```{r pssmooth  }
rice.pub.yr <- rice.pub.cl.mo %>% 
     tq_transmute(select=amount,
		  mutate_fun=to.yearly,
		  FUN=median)
```
now let's plot it


```{r smplot  }
rice.pub.yr %>% 
    ggplot(aes(x=year(yrmon),y=amount))+
	    geom_line()
```

its too zig zagy

let's try whether ma can smooth it further


```{r mas  }
rice.pub.yr %>% 
    tq_transmute(select=amount,
		 mutate_fun=SMA,
		 n=3,
		 col_rename="amount") %>% 
    filter(!is.na(amount)) %>% 
    ggplot(aes(x=year(yrmon),y=amount)) +
	   geom_line()
```


the smoothening clearly shows that there is recent downward trend


let's use the same mechanism in monthly date

```{r mos  }
rice.pub.ma <- rice.pub.cl.mo %>% 
	    tq_transmute(select=amount,
		 mutate_fun=SMA,
		 n=3,
		 col_rename="amount") %>% 
		filter(!is.na(amount))
```

now let's smoothen it


```{r mos2  }
rice.pub.ma %>% 
    ggplot(aes(x=yrmon,y=amount))+
    geom_line()
```

Let's increase the windown



```{r inw  }
rice.pub.cl.mo %>% 
	    tq_transmute(select=amount,
		 mutate_fun=SMA,
		 n=10,
		 col_rename="amount") %>% 
		filter(!is.na(amount)) %>% 
		ggplot(aes(x=yrmon,y=amount))+
		    geom_line()

```

okay, good, it smoothened quite a bit

let's increase it even further

```{r inw  }
rice.pub.cl.mo %>% 
	    tq_transmute(select=amount,
		 mutate_fun=SMA,
		 n=20,
		 col_rename="amount") %>% 
		filter(!is.na(amount)) %>% 
		ggplot(aes(x=yrmon,y=amount))+
		    geom_line() +
		    geom_smooth(method="lm")

```

let's have a MA over the last three years


```{r inw2  }
rice.pub.cl.mo %>% 
    filter(year(yrmon) > 2013) %>% 
	    tq_transmute(select=amount,
		 mutate_fun=SMA,
		 n=3,
		 col_rename="amount") %>% 
		filter(!is.na(amount)) %>% 
		ggplot(aes(x=yrmon,y=amount))+
		    geom_line() +
		    geom_smooth(method="lm")

```

so it clearly shows that there is a downward trend for last three years of public stock

let's zoom into last five years


```{r pubstock5  }
rice.pub.cl.mo %>% 
    filter(year(yrmon)>2011) %>% 
    ggplot(aes(x=yrmon,y=amount)) +
	    geom_line()
```


let's zoom further, how about last two years


```{r pubstock2  }
rice.pub.cl.mo %>% 
    filter(year(yrmon)>2014) %>% 
    ggplot(aes(x=yrmon,y=amount)) +
	    geom_line()
```

how about three years?


```{r pubstock3  }
rice.pub.cl.mo %>% 
    filter(year(yrmon)>2013) %>% 
    ggplot(aes(x=yrmon,y=amount)) +
	    geom_line()
```




Lets' have a look at year-wise distribution


```{r ps3  }
rice.pub.cl.mo %>% 
    filter(year(yrmon) > 2012) %>% 
    ggplot(aes(x=month(yrmon),y=amount))+
    geom_line() +
    facet_wrap(~year(yrmon))
```

## FOOD GRAIN PROCUREMENT

### AMAN 

```{r ps4  }
url  <- read_html("http://fpmu.gov.bd/fpmu-database/0301.htm")
aman.proc.raw <- url %>% 
            html_node("table") %>% 
	    html_table(fill=TRUE) %>% 
	    slice(8:29)

var.aman.proc <- c("year","paddy.tar","rice.tar","rice.in.tar", 
			"paddy.act","rice.act","rice.in.act",
			"paddy.price","rice.price.pbl","rice.price.atp",
			"proc.start", "proc.close")

names(aman.proc.raw)  <- var.aman.proc
aman.proc <- aman.proc.raw %>% 
		mutate_at(vars(-year,-proc.start,-proc.close), as.numeric)
save(aman.proc, file="./RDATA/aman_proc.RData")
```

### BORO

```{r borop  }
url  <- read_html("http://fpmu.gov.bd/fpmu-database/0302.htm")
boro.proc.raw  <- url %>% 
		    html_node("table") %>% 
		    html_table(fill=TRUE) %>% 
		    slice(8:29)

var.boro.proc <- c("year","paddy.tar","rice.tar","rice.in.tar", 
			"paddy.act","rice.act","rice.in.act",
			"paddy.price","rice.price",
			"proc.start", "proc.close")

names(boro.proc.raw)  <- var.boro.proc

boro.proc <- boro.proc.raw %>% 
		mutate_at(vars(-year,-proc.start,-proc.close), as.numeric)
	    
save(boro.proc, file="./RDATA/boro_proc.RData")

```

###  Month-wise rice procurement

let's collect data on month-wise rice procurement

```{r moproc  }
url  <- read_html("http://fpmu.gov.bd/fpmu-database/0304.htm")
rice.proc.mo.raw <- url %>% 
		    html_node("table") %>% 
		    html_table(fill=TRUE) %>% 
		    slice(5:17)
names(rice.proc.mo.raw)  <- rice.proc.mo.raw %>% slice(1)
rice.proc.mo.df  <- rice.proc.mo.raw %>% 
		    slice(-1) 
```

Now time to tidy up things

```{r mpt  }
rice.proc.mo.td <- rice.proc.mo.df %>% 
	    gather(FY,amount,-Month)

rice.proc.mo.td2  <- rice.proc.mo.td %>% 
		mutate(year=ifelse(Month %in% c("July","August","September","October","November","December"),sub("(.+)\\/(.+)","\\1",FY),sub("(.{2})(.+)\\/(.+)","\\1\\3",FY))) %>% 
		select(-FY) %>% 
		mutate(year=replace(year, year=="1900", "2000")  ,
		       yrmon=paste(year,Month,sep="-"),
		       yrmon=as.yearmon(yrmon,format="%Y-%B"),
		       amount=as.numeric(amount)
		       )  %>% 
		select(yrmon,amount)
save(rice.proc.mo.td2, file="./RDATA/rice_proc_mo_td2.RData")

```

### District wise procurement

```{r distproc  }
url  <- read_html("http://fpmu.gov.bd/fpmu-database/0307.htm")
proc.dist.raw  <- url %>% 
		html_node("table") %>% 
		html_table(fill=TRUE)
save(proc.dist.raw, file="./RDATA/proc_dist_raw.RData")
```


# IMPORTS of RICE

## Yearly imports

let's bring in the data first

```{r impy  }
url  <- read_html("http://fpmu.gov.bd/fpmu-database/0501.htm")
rice.yr.imp.raw <- url %>% 
               html_node("table") %>% 
	       html_table(fill=TRUE) %>% 
	       slice(7:33)
var.rice.yr.imp <- c("FY","rice.aid","wheat.aid","total.aid",
		     "rice.gob.comm","wheat.gob.comm","total.gob.comm",
		     "rice.tot.gob.imp","wheat.tot.gob.imp","total.gob.imp",
		     "rice.pri.imp","wheat.pri.imp","total.pri.imp", 
		     "rice.national.imp","wheat.national.imp","total.national.imp")
names(rice.yr.imp.raw)  <- var.rice.yr.imp
rmcom <- function(x) {sub(",","",x)}
rice.yr.imp <- rice.yr.imp.raw %>% 
		 mutate_all(funs(rmcom)) %>% 
                 mutate_at(vars(-FY),as.numeric) %>%
		 mutate(FY=sub("\\*$","",FY),
			FY=sub("(^\\d{2}).+(\\d{2}$)","FY\\2",FY),
			FY=factor(FY,levels=FY)
			)
save(rice.yr.imp, file="./RDATA/rice_yr_imp.RData")
		    
```

Now time to plot some of the import data

```{r imppl  }
load("./RDATA/rice_yr_imp.RData")
rice.yr.imp %>% 
    gather(key,value,-FY) %>% 
    ggplot(aes(x=FY,y=value,color=key)) +
	   geom_line(group="") +
	   facet_wrap(~key, ncol=3, scale="free_y")
```

